Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-18 Paper/paper.tex
Have added an explenation about state based rates from data
Have added literature

Game theory is the mathematical study of interactive decision making between rational decision makers \cite{Maschler2013}.
A game is a description of strategic interactions that includes the constraints on the actions that the players can take and on the players' interests.

@@

>>>>

The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
In \cite{A} an empirical study is undertaken and service rate slow down is identified.
Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
This effect is further identified in \cite{B,C} where for example the negative effect on patient outcome is revealed.
In \cite{D,E} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen \cite{Bevan2006, url1, url2}).

The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
In particular, the aim is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.

@@

Note that the inter-arrival and service rates are not state dependent.
These will serve as a base level for the state dependent rates used throughout the game theoretic models.
